### 2023-12-21 conclusions/imag.tex
Final version of my thesis

@@

\subsubsection{Environmental impact}

@@

The societal impacts are hard t

@@

>>>>

My personnal environmental impact was overall very low.

I was walking from home to the lab everyday, which almost has no carbon footprint, and determining such a number is impossible.

I was already in Portugal when my thesis started so there wasn't any trips to join there. Nevertheless, for the sake of having things to talk about, I'm going to take into account the personnal flights home. One way between Toulouse and Lisbon is estimated to have a carbon footprint of $234 kg\, eq.\,CO_2$. Having made a total of 7 trips, my total carbon footprint for traveling during this period is of about $1638 kg\, eq.\, CO_2$.

The computers I was working on were my owns, they both have an average power consumption of about $25W$ or $50W$ total. In Portugal, the average carbon footprint of $1kW\cdot h^{-1}$ of electricity is of about $60g\,eq.\,CO_2$ \cite{portugalElec}. I used my computers an average of 7 hours a day for an estimated 175 days of work. This accounts for a total of $6.125kW\cdot h^{-1}$ which makes a carbon footprint of $3 675g\,eq.\,CO_2$.

All this data added together makes a total of $1642kg\,eq.\,CO_2$ personnal carbon footprint over my thesis in Portugal. This number is quite high, but this is due to the plane trips, the computer consumption is negligeable in the end.

@@

\subsubsection{Environmental impact}\label{subsubsec:envImp}

@@

The societal of such a projects are quite hard to determines since it all depends on the ways it is used, which can be for basically anything that a \ac{NN} can do. Nevertheless, RGPD isn't a concern for the chip itself, the chip being completely isolated from the internet or any other connection as of itself.

Using this chip in embedded systems might increase the digital divide, as they would push more state of the art hardware to market and thus rendering old technologies less relevant. However, the examples in \cref{sec:motivation} are more seemless uses. The gait detection \cite{gaitDS,gaitDig,gait} could be used in a security camera, without the user having to do anything different. The camera stabilization \cite{videoStab} if integrated in a chip within a camera would record a better stabilized video.

The good or bad impacts of the chip depends on its use. For a quite farfetch analogy, nuclear power has been used to both make environment friendly fuel and bombs.

@@

The lab that hosted me during my master thesis doesn't have a policy concerning the envirnoment. \ac{INESC}-MN being a micro and nanofabrication lab, they own and run most of the machines required to fabricate chips. The machines are not state of the art and mostly used for prototyping, for the lab itself or for contracted companies. As explained in \cref{subsubsec:envImp}, those machines are very power hungry and thus explains why any other measures would be rendered useless next to this.
